Observations from Parallelising Three Maximum Common (Connected) Subgraph Algorithms

### 2017-11-27 paper/paper.tex
32

    \caption{Aggregate speedups from 32 threads on 16 hyper-threaded cores, shown as a function of
    sequential runtime, for each family supported by the clique algorithm.}\label{figure:cliqueas}
\end{figure}

>>>>

    \caption{Aggregate speedups from 32 threads, shown as a function of sequential runtime, for each
    family supported by the clique algorithm.}\label{figure:cliqueas}
\end{figure}
